Manifold Destiny - or how to rig an election

### 2024-01-07 presentation.qmd
app1234

@@

@@

[Application]({{< var shn2 >}})

@@

[xxx application]({{< var shn3 >}})

@@

[xxx application]({{< var shn4 >}})

@@

```{r, echo=F, warning=F, message=F}
#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

>>>>

[Application 2: Rigged election process simulator]({{< var shn2 >}})

@@

[Application 3: Rigged election analyzer]({{< var shn3 >}})

@@

@@

@@

[Application 4: Restoration of a rigged election]({{< var shn4 >}})

@@

```{r, echo=F, warning=F, message=F}
kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```
